\ZpL: a p-adic precision package

### 2018-02-03 ZpL/ZpL.tex
Add explicity the keyword "prec" in examples

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = ?{\color{function}\verb?random_element?}\verb?(?{\color{ring}\verb?Z3?}\verb?,5); x? \\
\cZpCR
 & \verb?...11111? \\
%\cZpFP
% & \verb?...00000000000000011111? \\
\cZpLC
 & \verb?...11111? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = ?{\color{function}\verb?random_element?}\verb?(?{\color{ring}\verb?Z2?}\verb?,10)? \\
 & \verb?y = ?{\color{function}\verb?random_element?}\verb?(?{\color{ring}\verb?Z2?}\verb?,5)? \\
\cIn
 & \verb?u, v = x+y, x-y? \\
 & \verb?u, v? \\
\cZpCR
 & \verb?(...10111, ...01111)? \\
\cZpLC
 & \verb?(...10111, ...01111)? \\
\end{tabular}}

@@

\noindent \textbf{Matrix multiplication.}
%
As revealed in \cite{caruso-roe-vaccon:15}, a first simple example where 
this phenomenon appears is simply matrix multiplication.
This might be surprising because no division occurs in this situation.
Observe nevertheless the difference between \ZpCR and \ZpLC.

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
% & \verb?N = 4? \\
% & {\color{ring}\verb?Z2?}\verb? = Zp(2, prec=50, print_mode="digits")? \\
% & {\color{ring}\verb?Q2?}\verb?=?{\color{ring}\verb?Z2?}\verb?.fraction_field()? \\
 & \verb?S.<t> = ?{\color{constructor}\verb?PowerSeriesRing?}\verb?(?{\color{ring}\verb?Q2?}\verb?, 16)? \\
 & \verb?h = 1 + t + t^3? \\
 & \verb?y = t + t^2 * ?{\color{function}\verb?random_element?}\verb?(S,10)? \\
 & \verb?g = y.derivative() / h(y)? \\
 & \verb?u = ?{\color{function}\verb?Newton_Iteration_Solver?}\verb?(g, h, 4); u[15]? \\
\cZpCR
 & \verb?...1101? \\
\cZpLC
 & \verb?...11011101? \\
\end{tabular}}

@@

Unfortunately, the latter condition cannot be checked on the matrix 
$M_t$ (because of reductions). 
However it is possible (and easy) to check whether the weaker condition 
$d\Phi_{t,\ttv}(K_t) \subsetneq p^N \Zp$. This checking is achieved by 
the method
\verb?is_precision_capped? (provided by our package) which returns true 
if $d\Phi_{t,\ttv}(K_t) = p^N \Zp$. As a consequence, when this method
answers false, the absolute precision computed by the software is
likely optimal.
\end{rmk}

>>>>

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = ?{\color{function}\verb?random_element?}\verb?(?{\color{ring}\verb?Z3?}\verb?, prec=5); x? \\
\cZpCR
 & \verb?...11111? \\
%\cZpFP
% & \verb?...00000000000000011111? \\
\cZpLC
 & \verb?...11111? \\
\end{tabular}}

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
 & \verb?x = ?{\color{function}\verb?random_element?}\verb?(?{\color{ring}\verb?Z2?}\verb?, prec=10)? \\
 & \verb?y = ?{\color{function}\verb?random_element?}\verb?(?{\color{ring}\verb?Z2?}\verb?, prec=5)? \\
\cIn
 & \verb?u, v = x+y, x-y? \\
 & \verb?u, v? \\
\cZpCR
 & \verb?(...10111, ...01111)? \\
\cZpLC
 & \verb?(...10111, ...01111)? \\
\end{tabular}}

@@

\noindent \textbf{Matrix multiplication.}
%
As revealed in \cite{caruso-roe-vaccon:15}, a first simple example where 
unstability appears is simply matrix multiplication.
This might be surprising because no division occurs in this situation.
Observe nevertheless the difference between \ZpCR and \ZpLC.

@@

{\noindent \small
\begin{tabular}{rl}
\cIn
% & \verb?N = 4? \\
% & {\color{ring}\verb?Z2?}\verb? = Zp(2, prec=50, print_mode="digits")? \\
% & {\color{ring}\verb?Q2?}\verb?=?{\color{ring}\verb?Z2?}\verb?.fraction_field()? \\
 & \verb?S.<t> = ?{\color{constructor}\verb?PowerSeriesRing?}\verb?(?{\color{ring}\verb?Q2?}\verb?, 16)? \\
 & \verb?h = 1 + t + t^3? \\
 & \verb?y = t + t^2 * ?{\color{function}\verb?random_element?}\verb?(S, prec=10)? \\
 & \verb?g = y.derivative() / h(y)? \\
 & \verb?u = ?{\color{function}\verb?Newton_Iteration_Solver?}\verb?(g, h, 4); u[15]? \\
\cZpCR
 & \verb?...1101? \\
\cZpLC
 & \verb?...11011101? \\
\end{tabular}}

@@

Unfortunately, the latter condition cannot be checked on the matrix 
$M_t$ (because of reductions). 
However it is possible (and easy) to check whether the weaker condition 
$d\Phi_{t,\ttv}(K_t) \subsetneq p^N \Zp$. This checking is achieved by 
the method
{\color{method}\verb?is_precision_capped?} (provided by our package) which returns true 
if $d\Phi_{t,\ttv}(K_t) = p^N \Zp$. As a consequence, when this method
answers false, the absolute precision computed by the software is
likely optimal.
\end{rmk}
